Big_map

### 2022-10-17 graphs_newt_snakes/big_map.Rmd
Looking at how differt grid values, cost values, and map size impast newt and snake coevolution. More wrtiing too come.

@@

big_map_tall<- read.csv("~/Desktop/big_map/all_lit.txt" , header = TRUE)

@@

big_map_cor<- read.csv("~/Desktop/big_map/all_cor.txt" , header = TRUE)
big_map_cor$group_rep <- paste0(big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd,"_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd, "_", big_map_cor$rep)
big_map_cor$group <- paste0(big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd,"_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd)
big_map_cor$sim=LETTERS[factor(big_map_cor$group)]
big_map_cor$snake_newt_rep <- paste0("Snake_",big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd, "_Newt_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd, "_", big_map_cor$rep)

big_map_grid<-read.csv("~/Desktop/big_map/all_grid.txt" , header = TRUE)
big_map_grid$group <- paste0(big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd,"_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd)
big_map_grid$group_rep <- paste0(big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd,"_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd, "_", big_map_grid$rep)

big_map_grid$sim=LETTERS[factor(big_map_grid$group)]
big_map_grid$snake_newt_rep <- paste0("Snake_",big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd, "_Newt_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd, "_", big_map_grid$rep)

@@

### Phenotype differences
```{r, whale}
min_gen=100
max_gen=10000
rep=0

@@

ginmin = 100
ginmax = 10000

@@

cor_trends_by_gen(big_map_tall, big_map_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=10000, pattern=GA1_pattern[myrandomlist[1]])

@@

min_gen=100
max_gen=10000
GA_summary(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

@@

min_gen=100
max_gen=10000

@@

### By Snake GA 
```{r, snakega plots summary 1}
min_gen=100
max_gen=10000
#

@@

### By Newt GA 
```{r, newtga plots summary 1}
min_gen=100
max_gen=10000
#

@@

min_gen=100
max_gen=10000
#heatmap
build_heatmap(big_map_tall, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype 
```{r, early plots Heatmap pheno 1}
min_gen=100
max_gen=10000
build_heatmap(big_map_tall, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

>>>>

```{bash, data file gathering longer run}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=big_map_30
thefolder=${thepath}${foldername}/*

@@

big_map_tall<- read.csv("~/Desktop/big_map/all_lit.txt" , header = TRUE)
filter_col=grepl( "X" , names( big_map_tall ))
big_map_tall= big_map_tall[, filter_col==FALSE]
big_map_tall_30<- read.csv("~/Desktop/big_map_30/all_lit.txt" , header = TRUE)
big_map_tall_30$rep=1
big_map_tall<-rbind(big_map_tall, big_map_tall_30)

@@

big_map_cor<- read.csv("~/Desktop/big_map/all_cor.txt" , header = TRUE)
filter_col=grepl( "X" , names( big_map_cor ))
big_map_cor= big_map_cor[, filter_col==FALSE]
big_map_cor_30<- read.csv("~/Desktop/big_map_30/all_cor.txt" , header = TRUE)
big_map_cor_30$rep=1
big_map_cor<-rbind(big_map_cor, big_map_cor_30)
big_map_cor$group_rep <- paste0(big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd,"_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd, "_", big_map_cor$rep)
big_map_cor$group <- paste0(big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd,"_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd)
big_map_cor$sim=LETTERS[factor(big_map_cor$group)]
big_map_cor$snake_newt_rep <- paste0("Snake_",big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd, "_Newt_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd, "_", big_map_cor$rep)

big_map_grid<-read.csv("~/Desktop/big_map/all_grid.txt" , header = TRUE)
filter_col=grepl( "X" , names( big_map_grid ))
big_map_grid= big_map_grid[, filter_col==FALSE]
big_map_grid_30<- read.csv("~/Desktop/big_map_30/all_grid.txt" , header = TRUE)
big_map_grid_30$rep=1
big_map_grid<-rbind(big_map_grid, big_map_grid_30)
big_map_grid$group <- paste0(big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd,"_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd)
big_map_grid$group_rep <- paste0(big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd,"_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd, "_", big_map_grid$rep)
big_map_grid$sim=LETTERS[factor(big_map_grid$group)]
big_map_grid$snake_newt_rep <- paste0("Snake_",big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd, "_Newt_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd, "_", big_map_grid$rep)

@@

### Phenotype differences
```{r, whale}
min_gen=100
max_gen=30000
rep=1

@@

ginmin = 100
ginmax = 30000

@@

cor_trends_by_gen(big_map_tall, big_map_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=30000, pattern=GA1_pattern[myrandomlist[1]])

@@

min_gen=100
max_gen=30000
GA_summary(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

@@

min_gen=100
max_gen=30000

@@

### By Snake GA 
```{r, snakega plots summary 1}
min_gen=100
max_gen=30000
#

@@

### By Newt GA 
```{r, newtga plots summary 1}
min_gen=100
max_gen=30000
#

@@

min_gen=100
max_gen=30000
#heatmap
build_heatmap(big_map_tall, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype 
```{r, early plots Heatmap pheno 1}
min_gen=100
max_gen=30000
build_heatmap(big_map_tall, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```
